Ion pairing controls rheological properties of ``crocodile-line'' polyelectrolyte hydrogels

### 2016-01-29 PALSE/ion_pairing_paper.tex
no empty circle in fig:dissociation better caption

\begin{figure}
\includegraphics{dissociation.pdf}
\caption{Crocodile line model. (a) Sketch of the network in the case of a crocodile line of size $n=3$ between cross-links (gray disks) and a persistence length $r_\mathrm{src}\approx 3D$. Empty circles are not individual monomers but electrostatic blobs of size $D$. Electrostatic blobs containing an anionic head are shown as black filled circles. (b) Relation between the number of monomers between uncondensed charges and the number of chains between cross-link points. Full circles are obtained from (Eq.~\ref{eq:A}) in its validity domain. Empty circles are obtained for \ce{PIm+Br-} either via (Eq.~\ref{eq:A}) outside its validity or by extrapolation of the solid line that corresponds to $n = A^2$.}
\label{fig:dissociation}
\end{figure}

@@

The only unknown here is the reduced temperature $\tau$, possibly different between poly(pyrrolidinium) based and poly(immidazolium) based polymers. We know that the undissociated chain has a $\Theta$ temperature higher than \SI{100}{\celsius}, thus $0.2<\tau<1$. In addition, we must have $A\geq 1$, which implies through (Eq.~\ref{eq:A}) $\tau\leq 0.235$, corresponding to $\Theta\approx\SI{116}{\celsius}$. This limit value yields $A=1$ for both \ce{PPyr+I-} and \ce{PPyr+Br-}, indicating full dissociation of the cationic moieties. By contrast \ce{PPyr+Cl-} has a charge every 7 monomers. Supposing the same $\tau$, \ce{PIm+I-} has a dissociated ion pair every 10 monomers, see Table~\ref{tab:results}. Of course analysing \ce{PIm+Br-} based on the value of $\gamma_c$ gives an inconsistent value $A=3.4$ indicating that the hydrogel doesn't belong to the same regime.

>>>>

\begin{figure}
\includegraphics{dissociation.pdf}
\caption{Crocodile line model. (a) Sketch of the network in the case of a crocodile line of size $n=3$ between cross-links (gray disks) and a persistence length $r_\mathrm{src}\approx 3D$. Empty circles are not individual monomers but electrostatic blobs of size $D$. Electrostatic blobs containing an anionic head are shown as black filled circles. (b) Relation between the number of monomers between uncondensed charges and the number of chains between cross-link points. The solid line corresponds to $n = A^2$. Full circles are obtained from (Eq.~\ref{eq:A}). In the case of \ce{PIm+Br-}, we are not in the validity regime of (Eq.~\ref{eq:A}), and we have to extrapolate the solid line to estimate $A$ (dotted arrow).}
\label{fig:dissociation}
\end{figure}

@@

The only unknown here is the reduced temperature $\tau$, possibly different between poly(pyrrolidinium) based and poly(immidazolium) based polymers. We know that the undissociated chain has a $\Theta$ temperature higher than \SI{100}{\celsius}, thus $0.2<\tau<1$. In addition, we must have $A\geq 1$, which implies through (Eq.~\ref{eq:A}) $\tau\leq 0.235$, corresponding to $\Theta\approx\SI{116}{\celsius}$. This limit value yields $A=1$ for both \ce{PPyr+I-} and \ce{PPyr+Br-}, indicating full dissociation of the cationic moieties. By contrast \ce{PPyr+Cl-} has a charge every 7 monomers. Supposing the same $\tau$, \ce{PIm+I-} has a dissociated ion pair every 10 monomers, see Table~\ref{tab:results}. Of course analysing \ce{PIm+Br-} based on the value of $\gamma_c$ gives an inconsistent value $A=3.4$ indicating that this hydrogel doesn't belong to the same regime.
